Influence of Connectivity on Dung Beetle Communities

### 2025-05-29 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
editing figures

>>>>

results text blah blah (@sp_richness_patches)

```{r  label = sp_richness_patches, echo = FALSE, fig.cap = "Dung beetle secies richness in three different.....and the forest matrix surrounding patches.", out.width = '75%'}
knitr::include_graphics("corridor_docs/eric_ms_thesis/images/sp_richness_patches.png")
```
### Species diversity
